Insights Into Computational Reproducibility in Plant Pathology and a Way Forward

### 2020-12-07 analysis/paper/paper.Rmd
Rename or add section and subsection headers
Edit introduction and first paragraph of m&m

Therefore our definition of reproducibility will be that the computer code and data are made freely available to others for verification and conducting alternate analyses or for use in instructional purposes and that software used are also easily obtainable and preferably open source to avoid licensing or other issues related to accessibility for end-users related to costs or non-standard file formats, etc.

@@

We conducted a survey of a broad selection of articles to represent a broad swathe of publications in our discipline to evaluate the status of reproducibility and open science in our field.
The journals represented both fundamental and applied areas as well as pathogen or other group specific publications.

We randomly selected 300 articles published from 2012 to 2018 across 21 journals (Table \@ref(tab:journals)) and assigned them scores reflecting their openness and reproducibility.
A list of randomly selected pages was assigned to a randomized list of the 21 journals where the page number fell within an article for the given journal.
In cases where an article was not suitable, _e.g._, a review or otherwise not related to plant pathology, the next article was selected until a suitable article was found.
Notes regarding the selection of articles can be found in the file, XXXX, available in this paper's repository.
The pages list was numbered from page one and went to page 150.
This was done since some journals restart their numbering with each issue and also ensures that the journal is more likely to have a page number corresponding to the randomly generated value.
This also assumes that there is no effect or bias on reproducibility based on the time of year that an article was published, since most journals start with page number one at the beginning of the year.
The list of journals was saved from Google's sheets as a comma separated value (CSV) file for later use and distribution in a research compendium.

@@

## Analysis

@@

## Results

@@

# A General Workflow

@@

>>>>

Therefore our definition of reproducibility will be that the computer code and data are made freely available to others for verification and conducting alternate analyses or for use in instructional purposes. And that the software used are also easily obtainable and preferably open source to avoid licensing or other issues related to accessibility for end-users related to costs or non-standard file formats, etc.

In an effort to understand where as a discipline we stand as plant pathologists in regards to open science and reproducible research, we conducted a survey of a broad selection of articles to represent a broad swathe of publications to evaluate our status.

@@

We randomly selected 300 articles published from 2012 to 2018 across 21 journals (Table \@ref(tab:journals)) and assigned them scores reflecting their openness and reproducibility.
The journals represented both fundamental and applied areas as well as pathogen or other group specific publications.
A list of randomly selected pages was assigned to a randomized list of the 21 journals where the page number fell within an article for the given journal.
In cases where an article was not suitable, _e.g._, a review or otherwise not related to plant pathology, the next article was selected until a suitable article was found.
Notes regarding the selection of articles can be found in the file, XXXX, available in this paper's repository.
The pages list was numbered from page one and went to page 150.
This was done since some journals restart their numbering with each issue and also ensures that the journal is more likely to have a page number corresponding to the randomly generated value.
This also assumes that there is no effect or bias on reproducibility based on the time of year that an article was published, since most journals start with page number one at the beginning of the year.
The list of journals was saved from Google's sheets as a comma separated value (CSV) file for later use and distribution in a research compendium.

@@

## Statistical analysis

@@

# Results

@@

## A General Workflow

@@

# Authors' contributions

# Data availability statement
